\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-11 paper/paper.tex
A couple small edits in Conclusion.

\section{Discussion}
\label{sec:Discussion}
This paper has shown how to model and make inference for the kind of product reliability data commonly found in the field.  Products with long lifetimes often have few failures and when failures do occur the cause is frequently unknown to the analyst.  The hierarchical GLFP model provides a unified framework to accurately model data with multiple failure modes, and provide a measure of uncertainty.  Moreover, when there are multiple brands within the same product class, the hierarchical approach allows the model to borrow strength from brands with lots of failures in order to fit and make inference for groups with little information.  This is extremely advantageous since many products have time (e.g., left truncation and right censoring) and resource constraints (unidentified failure modes) that limit the amount of information in the data.  This makes standard parametric lifetime models inaccurate and difficult to estimate using classical estimation techniques such as ML.

We should point out some assumptions made in this analysis. First, we assume exchangability of units within drive-models. This assumption is due to our ignorance about the causes of failure and of potentially important covariates. If we had information about distinguishing characteristics of the two identified failure modes, then we should use this information. Also, there could be many environmental or human-related factors that impact lifetime, such as operating conditions associated with location in the data center, which are likely confounded with drive-model.

Second, as discussed in subsection \ref{subsec:mod_assess}, if there are causes which lead to clusters of failures at spaced-out intervals, the proposed GLFP is not flexible enough. We assume the failures that occur from various causes can be approximately assigned to two phases of product life.  Heterogeneity observed across drive models is due to different combinations of the two lifetime distributions.  In practice there might be groups of products or individual brands that exhibit more than two failure modes.  Extending the GLFP model to incorporate more than two failure distributions or a mixture of different lifetime models is possible.  However, additional information about the failure modes or more informative priors may be necessary for model identification and estimation.

@@

Advances in technology have made computationally intensive Bayesian methods for fitting hierarchical models available to practitioners.  When there are many product groups and model parameters efficient MCMC algorithms, such as HMC, can speed up computation due to its joint updating scheme that efficiently explores the parameter space.  In addition, black box Bayesian software, like R Stan, makes programing HMC straightforward once the full model and likelihood are specified.  We hopes this makes the hierarchical GLFP model a useful tool for engineers and reliability analysts.

>>>>

\section{Discussion}
\label{sec:Discussion}
This paper has shown how to model and make inference for consumer product reliability data commonly found in the field.  Products with long lifetimes often have few failures and when failures do occur the cause is frequently unknown to the analyst.  The hierarchical GLFP model provides a unified framework to accurately model data with multiple failure modes, and provide a measure of uncertainty.  Moreover, when there are multiple brands within the same product class, the hierarchical approach allows the model to borrow strength from brands with lots of failures to make inference for groups with little information.  This is extremely advantageous since many products have time (left truncation and right censoring) and resource constraints (unidentified failure modes) that limit the information in the data.  This makes standard parametric lifetime models inaccurate and difficult to estimate using classical estimation techniques such as ML.

We should point out some assumptions made in this analysis. First, we assume exchangability of units within drive-models. This assumption is due to our ignorance about the causes of failure and of potentially important covariates. If we had information about distinguishing characteristics of the two identified failure modes we should use this information. Also, there could be many environmental or human-related factors that impact lifetime, such as operating conditions associated with location in the data center, which are likely confounded with drive-model.

Second, as discussed in subsection \ref{subsec: Model Assessment}, if there are causes which lead to clusters of failures at spaced-out intervals, the proposed GLFP is too rigid.  We assume the failures that occur from various causes can be approximately assigned to two phases of product life.  Heterogeneity observed across drive models is due to different combinations of these two lifetime distributions.  In practice there might be groups of products or individual brands that exhibit more than two failure modes.  Extending the GLFP model to incorporate more than two failure distributions or a mixture of different lifetime models is possible.  However, additional information about the failure modes or more informative priors may be necessary for model identification and estimation.

@@

Advances in technology have made computationally intensive Bayesian methods for fitting hierarchical models available to practitioners.  When there are many product groups (and model parameters) efficient MCMC algorithms, such as HMC, can speed up computation due to its joint updating scheme that efficiently explores the parameter space.  In addition, black box Bayesian software, like R Stan, makes programing HMC straightforward once the full model and likelihood are specified.  We hopes this makes the hierarchical GLFP model a useful tool for engineers and reliability analysts.
